|

### 2023-04-25 manuscript/Chapter2-appendix1.Rmd
update appendix1

---
title: |
     Online supporting information for \
     Hunting experience shapes individual foraging specialisation and predator-prey interactions in an online videogame

@@

# Model fit
fit <- readRDS(
  here::here("outputs", "02_outputs_models", "02B2_DHMLM.rds")
)

@@

knitr::include_graphics(here::here("outputs", "05_outputs_figures", "05_figureS1.png"))

@@

knitr::include_graphics(here::here("outputs", "05_outputs_figures", "05_figureS2.png"))

@@

```{r figS4, out.width = "100%", fig.cap = "**Figure S4.** Posterior median differences and 95% credible intervals between the parameter values of each predator experience level predicted by the MDHGLM. The test is displayed on the y axis (i.e. whether the group of interest has either a greater or smaller value), and the parameter value is displayed on the x axis. Each panel represent the experience level groups that are being compared."}

knitr::include_graphics(here::here("outputs", "05_outputs_figures", "05_figureS4.png"))

>>>>

---
title: |
     Hunting experience shapes individual foraging specialisation and predator-prey interactions in an online videogame: \
     Appendix 1

@@

# Model fit
fit <- readRDS(
  here::here("outputs", "01_outputs_models", "B2_DHMLM.rds")
)

@@

knitr::include_graphics(here::here("outputs", "04_outputs_figures", "appendix1_figureS1.png"))

@@

knitr::include_graphics(here::here("outputs", "04_outputs_figures", "appendix1_figureS2.png"))

@@

```{r figS3, out.width = "100%", fig.cap = "**Figure S3.** Posterior median differences and 95% credible intervals between the parameter values of each predator experience level predicted by the MDHGLM. The test is displayed on the y axis (i.e. whether the group of interest has either a greater or smaller value), and the parameter value is displayed on the x axis. Each panel represent the experience level groups that are being compared."}

knitr::include_graphics(here::here("outputs", "04_outputs_figures", "appendix1_figureS3.png"))
